Sea-ice and macrozooplankton distribution as determinants of top predator community structure in Antarctic winter

### 2024-06-07 analysis/paper/paper.qmd
Table 6

@@

>>>>

```{r}
#| label: tbl-predprey
#| tbl-cap: "Contingency table of predator and macrozooplankton clusters. Macrozooplankton cluster names (1, 2a, 2b, 3a, 3b) from @dietrich2021winter. Significant differences (p < 0.05) are indicated in bold with asterisks (post hoc analysis of the Pearson residuals)."

make_predpreytbl(read_obj("stations_clust"))

@@

<!-- Figure 1 was created using QGIS -->
